%-------------------------
% Resume in Latex
% Author : Huy Ho
% License : MIT
%------------------------


\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://alexhuyho.com/}{\Large Huy Ho}} & Email : \href{mailto:huyho114@gmail.com}{huyho114@gmail.com}\\
  \href{http://alexhuyho.com/}{http://www.alexhuyho.com} & Mobile : +1-714-456-5596 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {California State University Fullerton}{Fullerton, CA}
      {Barchelor of Science in Computer Science}{Fall. 2018 -- May. 2020}
    \resumeSubheading
      {Orange Coast College}{Costa Mesa, CA}
      {Associate of Science in Computer Programming}{Aug. 2014 -- July. 2017}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

      \resumeSubheading
        {National Resouce Center For Asian Language}{Fullerton, CA}
        {IT Specialist}{Aug 2019 - Present}
        \resumeItemListStart
          \resumeItem{Research}
            {Curriculum Framework Development is a program help bilingual professor to develop a better way to help student learn different language more efficiently.}
          \resumeItem{Technical Support}
            {Developing and maintaining website and social media. Troubleshooting technical issues in a timely manner to issues and requests}
        \resumeItemListEnd
  
      \resumeSubheading
        {Cal State University Fullerton}{Fullerton, CA}
        {Computer Lab Consultant}{Aug 2019 - Present}
        \resumeItemListStart
          \resumeItem{Technical Support}
            {Troubleshooting in a timely manner to technical issues and requests.
            Assist with the operation of lab computers, printers, and other facilities.}
          \resumeItem{Notifications}
            {Service for sending email, notifications.}
          
        \resumeItemListEnd
  
      \resumeSubheading
        {Tuan Nguyen PC}{Baria Vungtau, Vietnam}
        {Computer Repair Technician}{Sep 2012 - Mar 2013}
        \resumeItemListStart
          \resumeItem{Internet Specialist }
            {Setup well-functioning LAN/WAN and other networks and manage components (servers, IPs etc.) Manage security options in networks to maintain privacy and protection from attacks.}
          \resumeItem{Hardware Repair}
            {Using OEM equipments to repair a range of peripherals, including input devices, output devices, and data storage devices.}
          \resumeItem{Software Repair}
            {Building or configuring new hardware, installing and updating software packages, and creating and maintaining computer networks.}
        \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
\resumeSubHeadingListStart
    \resumeSubItem{CSUF Swap}
      {Flutter Application for exchange parking spot between students in Cal State Fullerton.}
    \resumeSubItem{Mobile Learning}
      {Open source app for Intelligent Learning Experiences Lab, enable student to learn course material better through text to speech quiz.}
    \resumeSubItem{University System}
      {Replicate Course Search and Enroll function from student portal to implement database concept and algorithms.}
    
  \resumeSubHeadingListEnd

% --------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Languages}{: Dart, C++, Html, SQL, Javascript, Python, Php}
   }
   \item{
    \textbf{Technologies}{: Flutter, Android, Github, Firebase, AWS}
  }

  %  \resumeSubItem{Languages}
  %     {Dart, C++, Html, SQL, Javascript, Python, Php.}
  %   \resumeSubItem{Technologies}
  %     {Flutter, Android, Github, Firebase, AWS.}
 \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}

